Deep Reinforcement Learning for Conservation Decisions

### 2022-06-03 manuscript/manuscript.Rmd
Small language edits

How could an RL agent be applied to empirical data?
One solution would be to train an agent on a simulation environment that approximates the fishery of interest then query the policy of the agent to find a quota for the observed stock.
To illustrate this, we examine the quota that would be recommended by our newly trained RL agent, above, against historical harvest levels of Argentine hake based on stock assessments from 1986 - 2014 [@ramlegacy, see Appendix D].
Hake stocks showed a marked decline throughout this period, while harvests decreased only in proportion [Fig 3].
In contrast, our RL agent would have recommended significantly lower quotas over most of the same interval, including the closure of the fishery as stocks were sufficiently depleted -- a stark contrast to the management policy evidenced in the historical catch.
Note that we have no way of knowing for sure if the RL quotas would have led to recovery, let alone a truly optimal harvest rate, because we can never know the "true model" of the Argentine hake dynamics.
We can confirm that fishery closures seen in the RL agent's solution is also considered optimal under the assumptions of constant escapement theory [@Reed1979] whenever the stock is below the biomass of maximum sustainable yield ($B_{MSY}$), and that most fisheries models of this stock [@ramlegacy] would suggest that the stock sizes observed in the latter two decades of the data are below that threshold.

>>>>

How could an RL agent be applied to empirical data?
One solution would be to train an agent on a simulation environment that approximates the fishery of interest then query the policy of the agent to find a quota for the observed stock.
To illustrate this, we examine the quota that would be recommended by our newly trained RL agent, above, against historical harvest levels of Argentine hake based on stock assessments from 1986 - 2014 [@ramlegacy, see Appendix D].
Hake stocks showed a marked decline throughout this period, while harvests decreased only in proportion [Fig 3].
In contrast, our RL agent would have recommended significantly lower quotas over most of the same interval, including the closure of the fishery as stocks were sufficiently depleted -- a stark contrast to the management policy evidenced in the historical catch.
Note that we have no way of knowing for sure if the RL quotas would have led to recovery nor do we know the optimal harvest rates, because we can never know the "true model" of the Argentine hake dynamics.
We can confirm that fishery closures seen in the RL agent's solution are considered optimal under the assumptions of constant escapement theory [@Reed1979] whenever the stock is below the biomass of maximum sustainable yield ($B_{MSY}$), and that most fisheries models of this stock [@ramlegacy] would suggest that the populations observed in the latter two decades of the data are below that threshold.
